Nanophotonic Computational Design

### 2013-02-24 defense/pres3.tex
Even closer...

\I  \bold{Realization}: Design-by-description is \emph{extremely powerful}
\pause
    \BI The description (or function) of all useful devices is known
    \I  Therefore, design-by-description enables the design of \emph{everything} 
    \EI
\pause
\I  \bold{Assumption}: Design-by-description can actually be made to work
\pause
\I  \bold{Our goal}: Make it work!

@@

\I TE mode converter
\smallfig{takeaway}
\I  Efficiency: 86.4\%
\I  Power in rejection mode (transmitted fundamental): 0.7\%
\I  250 nm silicon slab surrounded by silica
\newpage

\threeDfig{3Db_wgc_tm}
\nextpage

\I TM mode converter
\smallfig{wgc_tm}
\I  Efficiency: 76.9\%
\I  Power in rejection mode (transmitted fundamental): 1.0\%
\newpage

\threeDfig{3Db_spl_modal}
\nextpage

\I  Spatial mode splitter
\BI  Efficiency: 88.7\%, 77.4\% (0.27\%, 0.20\%) \EI
\medfig{spl_modal}
\newpage

\threeDfig{3Db_spl_tetm}
\nextpage

\I  TE/TM splitter
\BI  Efficiency: 87.6\%, 88.8\% (1.06\%, 0.58\%) \EI
\medfig{spl_tetm}
\newpage

\threeDfig{3Db_spl_wdm}
\nextpage

\I  Wavelength splitter
\BI  Efficiency: 83.2\%, 78.7\% (0.49\%, 1.66\%) \EI
\medfig{spl_wdm}
\newpage

\threeDfig{3Db_hub_3x3}
\nextpage

\I 3x3 hub (88.6\%, 90.6\%, 87.3\% efficiency)
\bigfig{hub_3x3}
\newpage

\threeDfig{3Db_hub_4x4}
\nextpage

\I 4x4 hub
\bigfig{hub_4x4_eps}
\newpage

\I Efficiency: 85.9\%, 88.1\%, 85.4\%, 84.3\%
\bigfig{hub_4x4}
\newpage

\threeDfig{3Db_hub_2x2x2}
\nextpage

\I 2x2x2 hub (77.6\%, 73.7\%, 75.7\%, 75.2\% efficiency)
\bigfig{hub_2x2x2}
\newpage

\threeDfig{3Db_fib_te}
\nextpage

\I fiber coupler (51.5\%)
\medfig{fib_te}
\newpage

\threeDfig{3Db_fib_pol}
\nextpage

\I fiber coupler mode splitter (32.6\%, 22.7\%)
\bigfig{fib_pol}
\newpage

\threeDfig{3Db_fib_wdm}
\nextpage

\I fiber coupler wdm (31.6\%, 28.6\%)
\bigfig{fib_wdm}
\newpage
\EI
\end{document}

>>>>

\I  \bold{Realization}: Design-by-description is \emph{extremely powerful}
\pause
    \BI The description (or function) of all useful devices is known
    \I  Therefore, design-by-description enables the design of \emph{everything} 
    \EI
\pause
\I  Also, does not require nanophotonic expertise
\pause
\I  \bold{Assumption}: Design-by-description can actually be made to work
\pause
\I  \bold{Our goal}: Make it work!

@@

\I  Final design, with actual (simulated) field
\smallfig{takeaway}
\I  Efficiency: 86.4\% (rejection: 0.7\%)
\I  Discrepancy in efficiency likely due to evanescent modes
\I  3D proof-of-principle for multi-mode on-chip components
    \BI with \emph{extremely} small device footprints \EI
\newpage

\oursection{Result 2: Mode converter (TM)}
\threeDfig{3Db_wgc_tm}
\I  Analogous to previous result, but with opposite polarization
\I  Demonstrates that we can work with (multiple) TM modes as well 
\nextpage

\I  Efficiency: 76.9\% (rejection: 1.0\%)
\smallfig{wgc_tm}
\I  Lower efficiency likely due to poor confinement of TM-polarized field
\I  Previously not demonstrated in litterature
\newpage

\oursection{Result 3: Spatial mode splitter}
\threeDfig{3Db_spl_modal}
\I  Key component needed to achieve multi-mode on-chip optics
\nextpage

\I  Efficiency: 88.7\%, 77.4\% (rejection: 0.27\%, 0.20\%)
\medfig{spl_modal}
\I  Previous designs in 2D, first design in 3D
\footnotetext{Y. Jiao, S. Fan, D. A. B.  Miller, Optics Letters (2005)}
\newpage

\oursection{Result 4: TE/TM splitter}
\threeDfig{3Db_spl_tetm}
\I  Shows that both polarizations can be controlled simultaneously
\I  Never before demonstrated, existence somewhat doubtful

\I  Efficiency: 87.6\%, 88.8\% (1.06\%, 0.58\%)
\medfig{spl_tetm}
\newpage

\oursection{Result 5: Wavelength splitter}
\threeDfig{3Db_spl_wdm}
\I  Splits 1550 nm and 1310 nm waveguide modes
\I  Large wavelength separation allows for small device footprint
\nextpage

\I  Efficiency: 83.2\%, 78.7\% (0.49\%, 1.66\%)
\medfig{spl_wdm}
\newpage

\oursection{Result 6: 3x3 hub}
\threeDfig{3Db_hub_3x3}
\I  Allows for overlapping ``optical traces''
\I  First demonstration in a single device
\nextpage

\I  Efficiency: 88.6\%, 90.6\%, 87.3\%
\bigfig{hub_3x3}
\I  Rejection modes no longer used for computational efficiency 
\newpage

\oursection{Result 7: 4x4 hub}
\threeDfig{3Db_hub_4x4}
\I  Pop quiz: Can you guess which trace goes where?
\nextpage

\I  Formulate answer as a 4-digit number 
\bigfig{hub_4x4_eps}
\newpage

\I  Efficiency: 85.9\%, 88.1\%, 85.4\%, 84.3\% (Answer: 3241)
\bigfig{hub_4x4}
\newpage

\oursection{Result 8: 2x2x2 hub}
\threeDfig{3Db_hub_2x2x2}
\I  Demonstrates that switching mechanism can be separately engineered 
    for different wavelengths (1550 nm and 1310 nm)
\I  2x2x2 = 2 inputs, 2 outputs, and 2 wavelengths
\nextpage

\I Efficiency: 77.6\%, 73.7\%, 75.7\%, 75.2\% 
\bigfig{hub_2x2x2}
\newpage

\oursection{Result 9: Compact fiber coupler}
\threeDfig{3Db_fib_te}
\I  Compact fiber core (2 um) used for computational efficiency
    \BI Refractive indices of fiber: $n_\text{core} = 1.6$, 
                                    $n_\text{cladding} = 1.5$ \EI
\I  Membrane etched halfway to increase out-of-plane symmetry breaking
\nextpage

\I  Efficiency: 51.5\%
\smallfig{fib_te_short}
\I  Highest efficiency compact fiber coupler
\I  Compact: Device combines coupling and focusing functions
\newpage

\oursection{Result 10: Mode-splitting fiber coupler}
\threeDfig{3Db_fib_pol}
\I  Both couples and splits linear and circular polarizations
    \BI 1310 nm wavelength used to make fiber multi-modal \EI
\nextpage

\I Efficiency: 32.6\%, 22.7\%
\bigfig{fib_pol}
\newpage

\oursection{Result 11: Wavelength-splitting fiber coupler}
\threeDfig{3Db_fib_wdm}
\I  A fusion of result 9 (fiber coupler) and result 5 (wavelength splitter)
\I  Shows the power of full-parameter design-by-description
\nextpage

\I  Efficiency: 31.6\%, 28.6\%
\bigfig{fib_wdm}
\newpage

\oursection{Results summary}
\stepwise{
\I  Variety of devices suggests all devices possible
    \BI Converters: both TE and TM polarizations
    \I  Splitters: spatial, polarization, wavelength
    \I  Hubs: 3x3, 4x4, 2x2x2
    \I  Fiber couplers: compact, mode-splitting, wavelength-splitting \EI
\step{
\I  Design-by-description is a key enabler
    \BI All 11 final results achieved in only 3 weeks
    \I  Of course, 7 years of development and 18 monts of programming\ldots \EI
}
\step{
\I  Individual design runtimes between 8-80 hours
    \BI Many future speedups possible at all levels \EI
}}

\oursection{One more thing\ldots}
\pause
\medfig{spl_wdm}
\I  Let's revisit our wavelength splitter 
\nextpage

\EI
\end{document}
